---
title: "Lab 10 Replication Notebook"
author: "Christopher Prener, Ph.D."
date: '(`r format(Sys.time(), "%B %d, %Y")`)'
output: 
  github_document: default
  html_notebook: default 
---

## Introduction
This is the replication notebook for Lab 10 from the course SOC 4650/5650: Introduction to GISc.

## Load Dependencies
The following code loads the package dependencies for our analysis:

```{r package-load}
# tidyverse packages
library(dplyr)   # data wrangling
library(readr)   # work with csv files

# other packages
library(here)    # file path management
library(sf)      # spatial data tools
```

## Load Data
We'll use data distributed with the `lecture-11` repository:

```{r load-data}
permits15 <- read_csv(here("data", "demoPermits", "permits2015.csv"))
permits16 <- read_csv(here("data", "demoPermits", "permits2016.csv"))
city <- st_read(here("data", "MO_BOUNDARY_Counties", "St_Louis_City.shp"), 
                    stringsAsFactors = FALSE)
county <- st_read(here("data", "MO_BOUNDARY_Counties", "St_Louis_County.shp"), 
                    stringsAsFactors = FALSE)
```

## Part 2
## Question 1
The following code uses the `rbind()` function from `base R` to combine our two shapefiles mapping the county boundaries for St. Louis City and County respectively:

```{r bind-counties}
counties <- rbind(city, county)
```

We can check to make sure these were bound appropriately by using the `glimpse()` function from `dplyr`:

```{r check-county-data}
glimpse(counties)
```

After binding them and ensuring that the data matched, we will export them:

```{r export-county-data}
dir.create(here("data", "cleanData"))
st_write(counties, here("data", "cleanData", "StLouis_Regional_Counties.shp"), delete_dsn = TRUE)
```

### Question 2
The following code uses the `bind_rows()` function from `dplyr` to combine our two data tables containing demolition permit data:

```{r bind-demo-permits}
permits <- bind_rows(permits15, permits16)
```

We can check to make sure these were bound appropriately by using the `glimpse()` function from `dplyr`:

```{r check-demo-data}
glimpse(permits)
```

After binding them and ensuring that the data matched, we will export them:

```{r export-demo-data}
write_csv(permits, here("data", "cleanData", "demoPermits.csv"))
```
